Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl

### 2023-05-03 src/tex/ms.tex
Fix date
Typo
Fix typo in table

\title{Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl}
\author[1,2]{Miles Cranmer}
\affil[1]{Princeton University, Princeton, NJ, USA}
\affil[2]{Flatiron Institute, New York, NY, USA}
\date{\today}

@@

    However, complexity in \pysr is a completely user-configurable. We argue that the best definition for a ``simple'' expression is the one that is most interpretable by the user. An expression containing a dilogarithm may look commonplace to the particle physicist---and in fact be a great prior over the space of models for certain particle physics data---but extremely unusual to the fluid dynamicist, and perhaps not coincidentally a bad choice of prior for fluids data.
}

@@

\newcommand\extranotes{
& Expressivity scores: (1a) Inflexible basis of fixed expressions, combined in a linear sum.
(1b) Pre-trained on equations generated from limited prior.
(2) Flexible basis of expressions, with variable internal coefficients.
(3) Any scalar tree, with binary and unary operators.
(4) Any scalar tree, with custom operators allowed.
(5) Any scalar tree, with n-ary operators.
(6) Scalar/vector/tensor expressions of any arity.
\\
$\ast$ & Note that the ``Symbolic Distillation'' method from~\cite{cranmerDiscoveringSymbolicModels2020} is not an algorithm itself; it can be applied to any SR technique. Applying this general method to a specific technique will inherit a {\color{green}$\checkmark$} from the Symbolic Distillation column, if given. However, in general, this technique is easiest with those methods which have deep learning export.\\
}

>>>>

\title{Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl}
\author[1,2]{Miles Cranmer}
\affil[1]{Princeton University, Princeton, NJ, USA}
\affil[2]{Flatiron Institute, New York, NY, USA}
\date{May 2, 2023}

@@

    However, complexity in \pysr is completely user-configurable. We argue that the best definition for a ``simple'' expression is the one that is most interpretable by the user. An expression containing a dilogarithm may look commonplace to the particle physicist---and in fact be a great prior over the space of models for certain particle physics data---but extremely unusual to the fluid dynamicist, and perhaps not coincidentally a bad choice of prior for fluids data.
}

@@

\newcommand\extranotes{
& Expressivity scores: (1a) Pre-trained on equations generated from limited prior.
(1b) Basis of fixed expressions, combined in a linear sum.
(2) Flexible basis of expressions, with variable internal coefficients.
(3) Any scalar tree, with binary and unary operators.
(4) Any scalar tree, with custom operators allowed.
(5) Any scalar tree, with n-ary operators.
(6) Scalar/vector/tensor expressions of any arity.
\\
$\ast$ & Note that the ``Symbolic Distillation'' method from~\cite{cranmerDiscoveringSymbolicModels2020} is not an algorithm itself; it can be applied to any SR technique. Applying this general method to a specific technique will inherit a {\color{green}$\checkmark$} from the Symbolic Distillation column, if given. However, in general, this technique is easiest with those methods which have deep learning export.\\
}
